Analyzing Performance Bottleneck in Graph Neural Network Training: An Experimental View

### 2020-07-23 Manuscript/ms.tex
Update section 2.
更新GAT的公式.
Update related work.

%! TEX root = ms.tex
%! TEX program = pdflatex
\documentclass{elsarticle}
\usepackage{geometry}
\geometry{left=3cm, right=3cm, top=2.5cm, bottom=2.5cm} 
\usepackage{lineno,hyperref}
\usepackage{amsmath, amsthm}
\usepackage{relsize}
\usepackage{booktabs}
\usepackage{lscape}
\usepackage{xcolor}
\usepackage{subfig}
\modulolinenumbers[5]
\bibliographystyle{elsarticle-num}

@@

\title{Analyzing Performance Bottleneck in Graph Neural Network Training: An Experimental View}
\author{Zhaokang Wang, Yunpan Wang, Chunfeng Yuan, Yihua Huang\corref{correspondingauthor}}
\cortext[correspondingauthor]{Corresponding author}
\ead{\{wangzhaokang, wangyp\}@smail.nju.edu.cn, \{cfyuan, yhuang\}@nju.edu.cn}
\address{State Key Laboratory for Novel Software Technology, Department of Computer Science and Technology, Nanjing University, Nanjing 210023, China}

>>>>

%! TEX root = ms.tex
%! TEX program = pdflatex
\documentclass{elsarticle}
\usepackage{geometry}
\geometry{left=3cm, right=3cm, top=2.5cm, bottom=2.5cm} 
\usepackage{lineno,hyperref}
\usepackage{amsmath, amsthm}
\usepackage{relsize}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{lscape}
\usepackage{xcolor}
\usepackage{subfig}
\modulolinenumbers[5]
\bibliographystyle{elsarticle-num}

@@

	\title{Analyzing Performance Bottleneck in Graph Neural Network Training: An Experimental View}
	\author{Zhaokang Wang, Yunpan Wang}%, Chunfeng Yuan, Yihua Huang\corref{correspondingauthor}}
	%	\cortext[correspondingauthor]{Corresponding author}
	\ead{\{wangzhaokang, wangyp\}@smail.nju.edu.cn}%}, \{cfyuan, yhuang\}@nju.edu.cn}
	\address{State Key Laboratory for Novel Software Technology, \\Department of Computer Science and Technology, Nanjing University, \\Nanjing 210023, China}

### 2020-07-23 Manuscript/sec6-related-work.tex
Update related work.

PyG \cite{PyG}, DGL \cite{DGL} designed the graph neural network system based on the message-passing model.
PyG \cite{PyG} built upon PyTorch and obtained high data throught with sparse GPU accleration by providing dedicated CUDA kernels
and mini-batch technologies. DGL \cite{DGL} supported a variety of computing backends (Tensorflow, MXNet, PyTorch) and leveraged
fusion kernel techniques, which combine message function with update function to provide further performance improvements compared to PyG \cite{PyG}.
NeuGraph \cite{ma2019_neugraph} proposed a new programming model, SAGA-NN(Scatter-ApplyEdge-Gather-ApplyVertex with Neural Networks), and achieved excellent
performance in a single machine with mutliple GPUs by using graph computation optimization such as data partitioning management, scheduling and parall mutli-gpu processing.
AliGraph \cite{zhu2019_aligraph} targetd at Attributed Heterogeneous Graph data model, disassembed each layer of GNN into there basic operations: Sampling, Aggregate and Combine,
and leveraged graph parition, spearate storage of attributes and the importance-base vertex caching strategy in storage layer.
In general, various optimization techniques are used in these GNN systems' design, but whether these optimization techniques match the bottlenecks of GNN performance is a question
worth studying.

>>>>

PyG \cite{PyG} and DGL \cite{DGL} both adopt the message-passing model as the underlying programming model for GNNs and support training big datasets with the sampling techniques.
PyG \cite{PyG} is built upon PyTorch and it uses optimized CUDA kernels for GNNs to achieve high performance.
DGL \cite{DGL} provides a group of high level user APIs and supports training GNNs with a variety of backends (Tensorflow, MXNet and PyTorch) transparently.
It also supports LSTM as the aggregation functions.
NeuGraph \cite{ma2019_neugraph} proposes a new programming model \emph{SAGA-NN} for GNNs.
It focuses on training big datasets efficiently without sampling.
It partitions the dataset sophisticatedly, schedules the training tasks among multiple GPUs and swaps the data among GPUs and the host asynchronously.
AliGraph \cite{zhu2019_aligraph} targets at training GNNs on big attributed heterogeneous graphs that are common in e-commerce platforms.
The graphs are partitioned among multiple nodes in a cluster and AliGraph trains GNNs on the graphs in a distributed way with system optimizations.
PGL \cite{pgl} is another graph learning framework from Baidu based on the PaddlePaddle platform.
